### 2016-06-29 publications/Journal/4a-allocation.tex
Some analysis of results added

   \includegraphics[width=\modelfraction\columnwidth]{fig/pholdtree_alloc_BF.pdf}
   \caption{PholdTree model breadth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_bfs}

   \includegraphics[width=\modelfraction\columnwidth]{fig/pholdtree_alloc_DF.pdf}
   \caption{PholdTree model depth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_dfs}
\end{figure}

>>>>

   \includegraphics[width=\modelfraction\columnwidth]{fig/pholdtree_alloc_BF.pdf}
   \caption{PholdTree model breadth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_bfs}
   \includegraphics[width=\modelfraction\columnwidth]{fig/pholdtree_alloc_DF.pdf}
   \caption{PholdTree model depth first allocation with 4 kernels.}
   \label{fig:PholdTree_model_dfs}
\end{figure}

After simulation, the traces can be visualized for both breadth-first and depth-first allocation.
Using a breadth-first allocation scheme, as shown in Figure~\ref{fig:pholdtree_visualize_parBFS}, we notice that many events get exchanged between cores.
This is caused by the high number of inter-core connections and the high number of events exchanged over these connections.
The number of connections between nodes at the same simulation core is also rather low.
Using a depth-first allocation scheme, however, as shown in Figure~\ref{fig:pholdtree_visualize_parDFS},

Simulation results are shown in Figure~\ref{fig:?} for both allocation schemes in combination with both synchronization protocols.
We see that for both synchronization protocols, the depth-first allocation is significantly better than breadth-first allocation.
This is what we expected: depth-first allocation maintains locality better than breadth-first allocation.

%TODO this paragraph is strange: is this really the case?
Interestingly, we see that optimistic synchronization is less influenced by the allocation than conservative synchronization.
This is likely caused due to the lower number of connections to take into account in conservative synchronization.
Whereas conservative synchronization needs to take into account even scarcely used connections, optimistic synchronization does not.
The same is true in the opposite direction, though, where optimistic synchronization is slower when a good allocation is chosen.
Conservative synchronization will then be able to make better estimates, whereas optimistic synchronization does not make estimations.
